Molecular transport in human pial perivasculature

### 2024-03-11 paper/main.tex
Add some Bedussi et al references.

\begin{itemize}
\item Vinje et al~\cite{vinje2021brain} and references therein illustrates the location and characteristics of human pial perivascular spaces.
\item Mestre et al~\cite{mestre2022periarteriolar} study the properties of pial perivascular spaces in detail in mice.
\item Mestre et al~\cite{mestre2018flow} measure and characterize pial perivascular transport and estimate flow magnitudes (in mice).
\item Bollman et al~\cite{bollmann2022imaging} image the human pial vasculature at high resolution (7T).
\item Hornkjøl et al~\cite{hornkjol2022csf} model CSF flow and solute transport in the human SAS and brain parenchyma. 
\item Mardal et al~\cite{mardal2022mathematical} give a succinct introduction to MRI-based computational brain modelling. 
\end{itemize}

>>>>

\begin{itemize}
\item Vinje et al~\cite{vinje2021brain} and references therein illustrates the location and characteristics of human pial perivascular spaces.
\item Mestre et al~\cite{mestre2022periarteriolar} study the properties of pial perivascular spaces in detail in mice.
\item Mestre et al~\cite{mestre2018flow} measure and characterize pial perivascular transport and estimate flow magnitudes (in mice).
\item Bakker and coauthors studied perivascular spaces at the brain surface in a series of papers. They found that paravascular spaces (in particular periarterial spaces) represented low-resistance pathways~\cite{bedussi2017paravascular}, in communication with the surrounding CSF-filled subarachnoid spaces~\cite{bedussi2018paravascular}.
\item Bollman et al~\cite{bollmann2022imaging} image the human pial vasculature at high resolution (7T).
\item Hornkjøl et al~\cite{hornkjol2022csf} model CSF flow and solute transport in the human SAS and brain parenchyma. 
\item Mardal et al~\cite{mardal2022mathematical} give a succinct introduction to MRI-based computational brain modelling. 
\end{itemize}
